Detecting Facial Expressions in Professional Tennis Matches

### 2017-07-28 Report06-12.Rmd
Time Taken Paragraph

COMMENT: Add a paragraph on time taken to find faces for each software

@@

```{r Type-Matches-Manual, fig.cap = "This table shows the amount potential faces that were found by the APIs and whether they compare to those annotated manually. Where the FALSE row denotes API Face potential facees do not coincide with manually annotated faces. The tables shows that Google found 46.96% of the Faces identified manually.\\label{tab:Type-Matches-Manual}"}

@@

pander(ct)
```

Visual inspection showed that the `r ALLmetaIMGnamed %>% filter(type=="Google",!matchesManual) %>% nrow()` potential faces noted in Table \@ref(tab:Type-Matches-Manual) that were found by Google but not found manually were actually faces, however they were not all of players, and some of these crowd members were beyond what would be expected of an emotion recognition application for tennis players. These were deemed unlikely to be detected and neglected during manual annotation.

Table \@ref(tab:Type-Matches-Manual) shows Animetrics had the least amount of potential faces that matched Manually annotated faces. Also, visual inspection of the `r ALLmetaIMGnamed %>% filter(type=="Animetrics",!matchesManual) %>% nrow()` potential faces that did not match manually annotated faces showed the Animetrics results contained many potential faces that were not faces.

>>>>

The amount of time taken for each software to process facial detetion on the individual images is presented in the histogram below:

```{r timeDensity, fig.cap="This density plots diplays the common lengths of time each API took to detect faces in each image. It can be seen that the\\label{fig:timeDensity}"}
times <- ALLmetaIMGnamed %>% filter(!duplicated(file), type!="Manual")
ggplot(times, na.rm=T) + 
  scale_color_manual(values = type.colours) +
  geom_density(aes(x=time.user.self, colour=type)) +
  xlab("Time Taken") +
  theme(panel.background = element_rect(fill="grey"))
```

@@

```{r TypeMatchesManual, results='asis', fig.cap = "\\label{tab:TypeMatchesManual}"}

@@

pander(ct, caption = "This table shows the amount potential faces that were found by the APIs and whether they compare to those annotated manually. Where the FALSE row denotes API Face potential facees do not coincide with manually annotated faces. The tables shows that Google found 46.96% of the Faces identified manually.")
```

Visual inspection showed that the `r ALLmetaIMGnamed %>% filter(type=="Google",!matchesManual) %>% nrow()` potential faces noted in Table \@ref(tab:TypeMatchesManual), that were found by Google but not found manually were actually faces, however they were not all of players, and some of these crowd members were beyond what would be expected of an emotion recognition application for tennis players. These were deemed unlikely to be detected and neglected during manual annotation.

Table \@ref(tab:TypeMatchesManual) shows Animetrics had the least amount of potential faces that matched Manually annotated faces. Also, visual inspection of the `r ALLmetaIMGnamed %>% filter(type=="Animetrics",!matchesManual) %>% nrow()` potential faces that did not match manually annotated faces showed the Animetrics results contained many potential faces that were not faces.
